---
title: "Making Slides using .mono[Rmd]"
subtitle: "Output to html and pdf"
author: "Your Name"
date: "April 1, 2021"
output:
  xaringan::moon_reader:
    css: ['default', 'metropolis', 'metropolis-fonts', 'my-css.css']
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: inverse, middle

```{R, setup, include = F}
library(pacman)
library(pagedown)
p_load(
  broom, tidyverse,
  ggplot2, ggthemes, ggforce, ggridges,
  latex2exp, viridis, extrafont, gridExtra,
  kableExtra, snakecase, janitor,
  data.table, dplyr,
  lubridate, knitr,
  estimatr, here, magrittr
)

# Define pink color
red_pink <- "#e64173"
turquoise <- "#20B2AA"
orange <- "#FFA500"
red <- "#fb6107"
blue <- "#3b3b9a"
green <- "#8bb174"
grey_light <- "grey70"
grey_mid <- "grey50"
grey_dark <- "grey20"
purple <- "#6A5ACD"
slate <- "#314f4f"
# Dark slate grey: #314f4f

# Knitr options
opts_chunk$set(
  comment = "#>",
  fig.align = "center",
  fig.height = 7,
  fig.width = 10.5,
  warning = F,
  message = F
)

options(crayon.enabled = F)
options(knitr.table.format = "html")

# theme for ggplot
# theme simple function obtained from:
#
# write my own theme 
# 

# Column names for regression results
reg_columns <- c("Term", "Est.", "S.E.", "t stat.", "p-Value")

# Tidy regression results table
tidy_table <- function(x, 
                       terms, 
                       highlight_row = 1,
                       highlight_color = "black", 
                       highlight_bold = T, 
                       digits = c(NA, 3, 3, 2, 5), title = NULL)
  {
  x %>%
    tidy() %>%
    select(1:5) %>%
    mutate(
      term = terms,
      p.value = p.value %>% format_pv()
    ) %>%
    kable(
      col.names = reg_columns,
      escape = F,
      digits = digits,
      caption = title
    ) %>%
    kable_styling(font_size = 20) %>%
    row_spec(1:nrow(tidy(x)), background = "white") %>%
    row_spec(highlight_row, bold = highlight_bold, color = highlight_color)
}
```

```{css, echo = F, eval = F}
@media print {
  .has-continuation {
    display: block !important;
  }
}
```

# Background

---
name: t1

# Title 1

## Today

- Welcome! Sample code can be found  [here](https://github.com/TakaakiKishida/rmarkdown-letter-slide).
- AAA: *Why are we here?* Think! 
- BBB: *What are we doing?* Think!
- .mono[Rmd]: Rmd is *powerful*.

## Upcoming

- Learn more .mono[Rmd].
- Build momentum.

## Long run

.hi[Goal:] Deepen understandings for .mono[markdown], .mono[html] and .mono[css].

---

name: t2

# Title 2

## What is the .mono[Rmd]?

.mono[Rmd] helps us make

- ABC

- EFG

- HIJ

--

It will probably be hard to get used to it at the beginning, but will be worth in the future.  

--

**Repeat**. It will probably be hard to get used to it at the beginning, but will be worth in the future.
---

layout: false
class: middle, inverse

# Practice

---
name: t3

# Title 3

## What is it?

The [.mono[R] project website](https://www.r-project.org):

> R is a free software environment for statistical computing and graphics. It compiles and runs on a wide variety of UNIX platforms, Windows and MacOS.

--

What does that mean?

- .mono[R] was created for the statistical and graphical work required by econometrics.

- .mono[R] has a vibrant, thriving online community (*e.g.*, [Stack Overflow](https://stackoverflow.com/questions/tagged/r)).

- Plus it's __free__ and __open source__.

---

layout: true
# Regression and causality

---

First, we need to generate some data.

```{r, ex_data, eval = T}
# Set seed
set.seed(12345)
# Set sample size
n <- 1e4

# Generate data
ex_df <- tibble(
  female = rep(c(0, 1), each = n/2),
  grad = runif(n, min = female/3, max = 1) %>% round(0),
  wage = 100 - 25 * female + 5 * grad + rnorm(n, sd = 3)
)
```

---

Now we can estimate our naïve regression

$$
\begin{align}
  \text{Wage}_i = \alpha + \beta \text{Grad}_i + \varepsilon_i
\end{align}
$$

--

`lm(wage ~ grad, data = ex_df)`


```{r, echo = F}
lm(wage ~ grad, data = ex_df) %>% 
  tidy() %>%
  select(1:4) %>%
  mutate(term = c("Intercept", "Graduate")) %>%
  kable(col.names = c("", "Coef.", "S.E.", "t stat"), 
        digits = 2)
```

---

Now we can estimate our causal regression

$$
\begin{align}
  \text{Wage}_i = \alpha + \beta_1 \text{Grad}_i + \beta_2 \text{Female}_i + \varepsilon_i
\end{align}
$$

--

`lm(wage ~ grad + female, data = ex_df)`


```{r, echo = F}
lm(wage ~ grad + female, data = ex_df) %>% tidy() %>%
  select(1:4) %>%
  mutate(term = c("Intercept", "Graduate", "Female")) %>%
  kable(col.names = c("", "Coef.", "S.E.", "t stat"), digits = 2)
```

---
layout: false

# Title 4

We use gapminder data.

```{r, echo = T}
library(gapminder)
dat <- gapminder %>% 
  group_by(year, continent) %>% 
  summarise(`Life Expectancy` = mean(lifeExp),
            Population = sum(as.numeric(pop))) %>% 
  rename(Year = year, Continent = continent)
```

---

# Title 5

```{r, dpi=300, fig.width=8, fig.height=4, eval = T}
ggplot(dat, aes(Year, `Life Expectancy`, color = Continent)) +
  geom_point() + theme_bw()
```

---

exclude: true

```{R, generate pdfs, include = F, eval = T}
pagedown::chrome_print("sample-slide.html", output = "sample-slide.pdf")
```
